---
title: "Setup Git/Github"
output: html_document
date: "2025-03-20"
---

Source: https://rfortherestofus.com/2021/02/how-to-use-git-github-with-r#:~:text=The%20most%20straightforward%20way%20to,you're%20good%20to%20go.


This is all info that can be found in the link above with video that shows you how to do each of these steps!


1) Step One 

  A) is to download Git (this is the software) and install it on your computer

      https://git-scm.com/downloads

  B) another part of step one is to setup a github account 
      https://github.com/  
      
2) Step Two Get R to talk to Git

```{r Configure Git}
#use this is a package that helps you talk to git (computer software) to install uncomment the line of code below and install and turn on package

#install.packages("usethis")
library(usethis)#turn on package

#now you are connecting r to git, insert your username and email connected to your account 
use_git_config(user.name="yourusername",user.email="yourgitemail")

```

3) Create a Git Repository

```{r Create a Git Repository}

#in order to do this you need to be working in a project. When you create a project you can select to automatically create a Git Repository

library(usethis)
use_git()#this automatically makes the repository and then looks at what exists in your projects and asks you if its ok to commit them and restart r. you respond with whatever number 1,2, or 3 that says yes commit them.


#After R restarts,  you should have a Git tab by your environment

```

4) Commit your project to Git

You do not need code for this, you can commit after any change you make to your script/markdown document, just save before you do. (this was unclear to me in the video, so that made making a new commit hard for me)


Go to the Git tab, if you save your script, you should have something in this tab now, select the box and click commit, this saves the version in git

5) Connecting R and GitHub

```{r Connect R and GitHub}
library(usethis)#dont have to do this if the library is already on from previous steps he just does this in the video

#then you are going to create what is called a github token,it is a short link created by github that connects git in R to github online

create_github_token()#running this opens a tab in github online, you rename the token then click generate. then copy and save the token

library(gitcreds)#so you can enter the token
gitcreds_set()#run this then paste in your token, this will allow you to sync between R studio and GitHub (website)

```

6) Put your project into GitHub
```{r Put your project into GitHub}
library(usethis)
use_github()#when you run this it sends your project into github and opens a link with the repository in a new window

#this didn't immediately work for me I had to go to my github and refresh to see the project

```

you can also create a repository in GitHub first, then copy the link and when you create a project you can create using version control, then your project will be connected to GitHub right away

7) Push your code to GitHub

you do this by saving your code, then committing the changes then pushing the code up, using the green push arrow in the Git tab. Once you do this when you click on the markdown file in GitHub you should see all the information you put
